% Here we have a section where you might choose to acknoweldge your family, fellow students, advisor, dog, etc.
%
%I would like to begin first and foremost by thanking my advisor (und Doktormutter), Professor Kate Jensen. She has had an incredibly positive impact on my life and influenced my trajectory after Williams more than anyone else. For that, I am eternally grateful and feel incredibly fortunate to have been able work with her throughout the year. I also want to thank mein Freund and esteemed colleague Felix Knollmann, whose dedication to his own thesis helped encourage me to produce my best (read: most aesthetically pleasing) work and refrain from the procrastination that plagues any long term project. Sorry I couldn't help you make your figures not brown. Next year I'll be perusing a graduate degree in materials science in Germany ---a path I never would even have considered were it not for Felix and Kate. 
%
%I also would like to thank my friends that have made my time at Williams such an enjoyable experience. From forging a bird painting with Sarah Ritzmann to trick Marshall Borrus to buying 10~lbs of grits at Wild Oats with Lucas Estrada, I'm blessed to have filled my, albeit scarce, free-time with such bizarre and memorable experiences. That lack of free time is in part a result of my career on the track team. I want to thank my coaches and teammates who have made these last four years such an incredible experience. Specifically, I want to thank coach Hoey and coach Barron, who may have taught me more about life than running itself. 
%
%I would also like to thank my labmates, especially Josh Kang, who taught me both how to cure silicone and analyze it. Also Abdullah Nasir. Further, I really appreciate all the engineering help from Michael Taylor and Jason Mativi. Without them, most of my work would not have been possible. 
%
%Lastly, I would like to thank my parents. For raising me to always be curious, allowing me to attend Williams, and always supporting me in whatever ways they can, I am extremely grateful and fortunate. 
%\pagebreak

\noindent I would like to begin first and foremost by thanking my advisor, Professor Katharine Jensen. Looking back, Kate has had an incredibly positive impact on me and helped influence my  life-trajectory after Williams more than anyone else. For that, I am eternally grateful. Undoubtedly, mein Freund and esteemed colleague Felix Knollmann has helped encourage me to produce my best (read: most aesthetic) work and refrain the procrastination that inevitably accompanies any long term project. Were it not for Katharine and Felix, I would never have even considered moving to Germany for graduate school.

Additionally, I would also like to thank my labmates, especially Josh Minwoo Kang, who taught me both how to cure silicone and analyze it. Also Abdullah Nasir. Furthermore,\\ I really appreciate all the engineering help from Michael Taylor and Jason Mativi. Without them, most of my work would not have been possible. 

I also would like to thank my friends that have made my time at Williams such an enjoyable experience. From forging a bird painting with Sarah Ritzmann (to trick Marshall Borrus) to buying 10~lbs of grits at Wild Oats with Lucas Estrada, I'm blessed to have filled my --- albeit, scarce --- free-time with such bizarre and memorable experiences. That lack of free time is in part a result of my career on the track team. I want to thank my coaches and teammates who have made these last four years such an incredible experience. Specifically, I want to thank coach Hoey and coach Barron, who may have taught me more about life than running itself. 

Lastly, I would like to thank my parents. For raising me to always be curious, allowing me to attend Williams, and always supporting me in whatever ways they can, I am extremely grateful and fortunate. 
